\pkg{hesim}: Health Economic Simulation Modeling and Decision Analysis

### 2021-07-24 manuscript.tex
Modify R style

\begin{Schunk}
\begin{Sinput}
R> tmat <- rbind(
+    c(NA, 1, 2),
+    c(NA, NA, 3),
+    c(NA, NA, NA)
+  )
R> colnames(tmat) <- rownames(tmat) <- c("Stable", "Progression", "Dead")
R> tmat
\end{Sinput}
\begin{Soutput}
            Stable Progression Dead
Stable          NA           1    2
Progression     NA          NA    3
Dead            NA          NA   NA
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> library("hesim")
R> library("data.table")
R> n_patients <- 1000
R> patients <- data.table(
+    patient_id = 1:n_patients,
+    age = rnorm(n_patients, mean = 45, sd = 7),
+    female = rbinom(n_patients, size = 1, prob = .51)
+  )
R> 
R> states <- data.table(
+    state_id = c(1, 2),
+    state_name = c("Stable", "Progression") 
+  )
R> 
R> strategies <- data.table(
+    strategy_id = 1:3,
+    strategy_name = c("SOC", "New 1", "New 2"),
+    soc = c(1, 0, 0),
+    new1 = c(0, 1, 0),
+    new2 = c(0, 0, 1)
+  )
R> 
R> hesim_dat <- hesim_data(
+    strategies = strategies,
+    patients = patients,
+    states = states
+  )
R> hesim_dat
\end{Sinput}
\begin{Soutput}
$strategies
   strategy_id strategy_name soc new1 new2
1:           1           SOC   1    0    0
2:           2         New 1   0    1    0
3:           3         New 2   0    0    1

@@

\begin{Schunk}
\begin{Sinput}
R> library("flexsurv")
R> n_trans <- max(tmat, na.rm = TRUE) 
R> wei_fits <- vector(length = n_trans, mode = "list")
R> f <- as.formula(Surv(time, status) ~ factor(strategy_name) + female + age)
R> for (i in 1:length(wei_fits)){
+    if (i == 3) f <- update(f, .~.-factor(strategy_name)) 
+    wei_fits[[i]] <- flexsurvreg(f, data = onc3, 
+                                 subset = (transition_id == i),
+                                 dist = "weibull")
+  }
R> wei_fits <- flexsurvreg_list(wei_fits)
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> utility_tbl <- stateval_tbl(
+    data.table(state_id = states$state_id,
+               mean = c(.8, .6),
+               se = c(0.02, .05)
+    ),
+    dist = "beta")
R> utility_tbl
\end{Sinput}
\begin{Soutput}
   state_id mean   se
1:        1  0.8 0.02
2:        2  0.6 0.05
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> medcost_tbl <- stateval_tbl(
+    data.table(state_id = states$state_id,
+               mean = c(2000, 9500),
+               se = c(2000, 9500)
+    ),
+    dist = "gamma")
R> medcost_tbl
\end{Sinput}
\begin{Soutput}
   state_id mean   se
1:        1 2000 2000
2:        2 9500 9500
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> drugcost_tbl <- stateval_tbl(
+    drugcost_dt,
+    dist = "fixed")
R> drugcost_tbl
\end{Sinput}
\begin{Soutput}
    strategy_id state_id time_id time_start time_stop   est
 1:           1        1       1       0.00      0.25  2000
 2:           1        1       2       0.25       Inf  2000
 3:           1        2       1       0.00      0.25  1500
 4:           1        2       2       0.25       Inf  1200
 5:           2        1       1       0.00      0.25 12000
 6:           2        1       2       0.25       Inf 12000
 7:           2        2       1       0.00      0.25  1500
 8:           2        2       2       0.25       Inf  1200
 9:           3        1       1       0.00      0.25 15000
10:           3        1       2       0.25       Inf 15000
11:           3        2       1       0.00      0.25  1500
12:           3        2       2       0.25       Inf  1200
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> transmod_data <- expand(hesim_dat,
+                          by = c("strategies", "patients"))
R> head(transmod_data)
\end{Sinput}
\begin{Soutput}
   strategy_id patient_id strategy_name soc new1 new2      age female
1:           1          1           SOC   1    0    0 46.26366      1
2:           1          2           SOC   1    0    0 50.49314      1
3:           1          3           SOC   1    0    0 35.52785      1
4:           1          4           SOC   1    0    0 58.88309      0
5:           1          5           SOC   1    0    0 53.66930      0
6:           1          6           SOC   1    0    0 53.40432      1
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> transmod <- create_IndivCtstmTrans(wei_fits, transmod_data,
+                                     trans_mat = tmat, n = n_samples,
+                                     uncertainty = "normal",
+                                     clock = "reset",
+                                     start_age = patients$age)
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> utilitymod <- create_StateVals(utility_tbl, n = n_samples, 
+                                 hesim_data = hesim_dat)
R> drugcostmod <- create_StateVals(drugcost_tbl, n = n_samples,
+                                  time_reset = TRUE, hesim_data = hesim_dat)
R> medcostmod <- create_StateVals(medcost_tbl, n = n_samples,
+                                 hesim_data = hesim_dat)
R> costmods <- list(Drug = drugcostmod,
+                   Medical = medcostmod)
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> ictstm <- IndivCtstm$new(trans_model = transmod,
+                           utility_model = utilitymod,
+                           cost_models = costmods)
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> ictstm$sim_disease(max_age = 100)
R> head(ictstm$disprog_)
\end{Sinput}
\begin{Soutput}
   sample strategy_id patient_id grp_id from to final time_start
1:      1           1          1      1    1  3     1   0.000000
2:      1           1          2      1    1  2     0   0.000000
3:      1           1          2      1    2  3     1   8.058198
4:      1           1          3      1    1  2     0   0.000000
5:      1           1          3      1    2  3     1  15.250551
6:      1           1          4      1    1  3     1   0.000000
   time_stop
1: 11.183651
2:  8.058198
3: 12.794488
4: 15.250551
5: 23.791357
6:  6.047286
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> library("ggplot2")
R> autoplot(ictstm$stateprobs_, labels = labs_indiv,
+           ci = FALSE) 
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> hesim_dat$patients <- data.table(
+    patient_id = 1:4,
+    grp_id = c(1, 1, 2, 2),
+    patient_wt = rep(1/4, 4),
+    age = c(55, 65, 55, 65),
+    female = c(1, 1, 0, 0),
+    grp_name = rep(c("Female", "Male"), 
+                   each = 2)
+  )
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> onc_pfs_os <- as_pfs_os(onc3, patient_vars = c("patient_id", "female", "age", 
+                                                 "strategy_name"))
R> onc_pfs_os[patient_id %in% c(1, 2)]
\end{Sinput}
\begin{Soutput}
   patient_id female      age strategy_name pfs_time pfs_status
1:          1      0 59.85813         New 2 2.420226          1
2:          2      0 62.57282         New 2 7.497464          0
   os_status   os_time
1:         1 14.620258
2:         0  7.497464
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> onc_pfs_os_soc <- onc_pfs_os[strategy_name == "SOC"]
R> fit_pfs_soc_wei <- flexsurvreg(
+    Surv(pfs_time, pfs_status) ~ female,
+    data = onc_pfs_os_soc,
+    dist = "weibull")
R> 
R> fit_os_soc_wei <- flexsurvreg(
+    Surv(os_time, os_status) ~  female,
+    data = onc_pfs_os_soc,
+    dist = "weibull")
R> 
R> psmfit_soc_wei <- partsurvfit(
+    flexsurvreg_list(pfs = fit_pfs_soc_wei, os = fit_os_soc_wei),
+    data = onc_pfs_os_soc
+  )
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> drugcost_tbl <- stateval_tbl(
+    drugcost_dt[time_start ==  0][, time_start := NULL],
+    dist = "fixed")
R> drugcost_tbl
\end{Sinput}
\begin{Soutput}
   strategy_id state_id   est
1:           1        1  2000
2:           1        2  1500
3:           2        1 12000
4:           2        2  1500
5:           3        1 15000
6:           3        2  1500
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> survmods_data <- expand(hesim_dat, by = c("strategies", "patients"))
R> head(survmods_data)
\end{Sinput}
\begin{Soutput}
   strategy_id patient_id strategy_name soc new1 new2 grp_id
1:           1          1           SOC   1    0    0      1
2:           1          2           SOC   1    0    0      1
3:           1          3           SOC   1    0    0      2
4:           1          4           SOC   1    0    0      2
5:           2          1         New 1   0    1    0      1
6:           2          2         New 1   0    1    0      1
   patient_wt age female grp_name
1:       0.25  55      1   Female
2:       0.25  65      1   Female
3:       0.25  55      0     Male
4:       0.25  65      0     Male
5:       0.25  55      1   Female
6:       0.25  65      1   Female
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> survmods_params <- create_params(psmfit_soc_wei, n = n_samples, 
+                                   uncertainty = "bootstrap", 
+                                   max_errors = 5, silent = TRUE)
R> survmods_params$pfs$coefs$scale <- cbind(survmods_params$pfs$coefs$scale,
+                                           coef_pfs_wei)
R> survmods_params$os$coefs$scale <- cbind(survmods_params$os$coefs$scale,
+                                          coef_os_wei)
R> survmods_params$pfs$coefs$scale[1:2, ]
\end{Sinput}
\begin{Soutput}
     (Intercept)     female      new1      new2
[1,]    1.784666 -0.1364781 0.1814189 0.2654431
[2,]    1.776743 -0.1173777 0.1390351 0.2907570
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> survmods_data[, ("(Intercept)") := 1]
R> survmods <- create_PsmCurves(survmods_params, 
+                               input_data = survmods_data)
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> psm <- Psm$new(survival_models = survmods,
+                 utility_model = utilitymod,
+                 cost_models = costmods)
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> times <- seq(0, 30, by = .1)
R> psm$sim_survival(t = times)
R> head(psm$survival_)
\end{Sinput}
\begin{Soutput}
   sample strategy_id patient_id grp_id patient_wt curve   t
1:      1           1          1      1       0.25     1 0.0
2:      1           1          1      1       0.25     1 0.1
3:      1           1          1      1       0.25     1 0.2
4:      1           1          1      1       0.25     1 0.3
5:      1           1          1      1       0.25     1 0.4
6:      1           1          1      1       0.25     1 0.5
    survival
1: 1.0000000
2: 0.9998540
3: 0.9993126
4: 0.9982992
5: 0.9967670
6: 0.9946815
\end{Soutput}
\end{Schunk}

\begin{Schunk}
\begin{Sinput}
R> autoplot(psm$survival_, 
+           labels = c(labs_cohort,
+                      list(curve = c("PFS" = 1, "OS" = 2))
+                      ),
+           ci = TRUE, ci_style = "ribbon")
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> psm$sim_stateprobs()
R> psm$stateprobs_[sample == 1 & patient_id == 1 & state_id == 2 & t == 12]
\end{Sinput}
\begin{Soutput}
   sample strategy_id patient_id grp_id patient_wt state_id  t
1:      1           1          1      1       0.25        2 12
2:      1           2          1      1       0.25        2 12
3:      1           3          1      1       0.25        2 12
        prob
1: 0.3215069
2: 0.3934037
3: 0.4148810
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> library("msm")
R> qinit <- matrix(0, nrow = 3, ncol = 3)
R> qinit[1, 2] <-  0.28; qinit[1, 3] <-  0.013; qinit[2, 3] <-  0.10
R> msm_fit <- msm(state_id ~ time, subject = patient_id, 
+                 data = onc3p[strategy_name == "SOC"],
+                 exacttimes = FALSE,
+                 covariates = ~ age + female,
+                 qmatrix = qinit, gen.inits = FALSE)
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> params_rr <- list(
+    lrr_12_est = c(soc = log(1), new1 = log(.80), new2 = log(.71)),
+    lrr_12_se = c(soc = 0, new1 = .03, new2 = .04),
+    lrr_13_est = c(soc = log(1), new1 = log(.90), new2 = log(.85)),
+    lrr_13_se = c(soc = 0, new1 = .02, new2 = .03)
+  )  
R> 
R> params_rr_def <- define_rng({
+    list(
+      rr_12 = lognormal_rng(lrr_12_est, lrr_12_se),
+      rr_13 = lognormal_rng(lrr_13_est, lrr_13_se)
+    )}, n = n_samples)
R> params_rr_rng <- eval_rng(params_rr_def, params_rr)
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> x_rr <- as.matrix(transmod_data[, .(soc, new1, new2)])
R> rr <- cbind(xbeta(x_rr, params_rr_rng$rr_12),
+              xbeta(x_rr, params_rr_rng$rr_13))
R> head(rr) 
\end{Sinput}
\begin{Soutput}
         [,1]      [,2]
[1,] 1.000000 1.0000000
[2,] 1.000000 1.0000000
[3,] 1.000000 1.0000000
[4,] 1.000000 1.0000000
[5,] 0.833283 0.9039595
[6,] 0.833283 0.9039595
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> pmat <- apply_rr(pmat_soc, rr = rr,
+                   index = list(c(1, 2), c(1, 3)))
R> tprobs <- tparams_transprobs(pmat, tpmat_id)
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> cdtstm <- CohortDtstm$new(trans_model = transmod,
+                            utility_model = psm$utility_model,
+                            cost_models = psm$cost_models)
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> wtp <- seq(0, 250000, 500) 
R> cea_ictstm <- cea(ce_sim_ictstm, dr_costs = .03, dr_qalys = .03, k = wtp)
R> cea_pw_ictstm <- cea_pw(ce_sim_ictstm, comparator = 1,
+                          dr_qalys = .03, dr_costs = .03,
+                          k = wtp)
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> icer(cea_pw_ictstm, k = 100000, labels = labs_indiv) %>%
+    format()
\end{Sinput}
\begin{Soutput}
             Outcome                     New 1
1: Incremental QALYs         0.52 (0.16, 0.90)
2: Incremental costs   62,551 (51,685, 70,389)
3:   Incremental NMB -11,003 (-42,132, 21,247)
4:              ICER                   121,345
                      New 2
1:        0.93 (0.58, 1.27)
2: 90,010 (77,342, 100,581)
3:  3,223 (-28,582, 33,456)
4:                   96,543
\end{Soutput}
\end{Schunk}

>>>>

\begin{Schunk}
\begin{Sinput}
R> tmat <- rbind(c(NA, 1, 2), c(NA, NA, 3), c(NA, NA, NA))
R> colnames(tmat) <- rownames(tmat) <- c("Stable", "Progression", "Dead")
R> tmat
\end{Sinput}
\begin{Soutput}
            Stable Progression Dead
Stable          NA           1    2
Progression     NA          NA    3
Dead            NA          NA   NA
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> library("hesim")
R> library("data.table")
R> n_patients <- 1000
R> patients <- data.table(
+    patient_id = 1:n_patients,
+    age = rnorm(n_patients, mean = 45, sd = 7),
+    female = rbinom(n_patients, size = 1, prob = .51)
+  )
R> states <- data.table(
+    state_id = c(1, 2),
+    state_name = c("Stable", "Progression") 
+  )
R> strategies <- data.table(
+    strategy_id = 1:3,
+    strategy_name = c("SOC", "New 1", "New 2"),
+    soc = c(1, 0, 0),
+    new1 = c(0, 1, 0),
+    new2 = c(0, 0, 1)
+  )
R> hesim_dat <- hesim_data(
+    strategies = strategies,
+    patients = patients,
+    states = states
+  )
R> hesim_dat
\end{Sinput}
\begin{Soutput}
$strategies
   strategy_id strategy_name soc new1 new2
1:           1           SOC   1    0    0
2:           2         New 1   0    1    0
3:           3         New 2   0    0    1

@@

\begin{Schunk}
\begin{Sinput}
R> library("flexsurv")
R> n_trans <- max(tmat, na.rm = TRUE) 
R> wei_fits <- vector(length = n_trans, mode = "list")
R> f <- as.formula(Surv(time, status) ~ factor(strategy_name) + female + age)
R> for (i in 1:length(wei_fits)){
+    if (i == 3) f <- update(f, .~.-factor(strategy_name)) 
+    wei_fits[[i]] <- flexsurvreg(f, data = onc3, 
+      subset = (transition_id == i), dist = "weibull")
+  }
R> wei_fits <- flexsurvreg_list(wei_fits)
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> utility_tbl <- stateval_tbl(
+    data.table(
+      state_id = states$state_id,
+      mean = c(.8, .6),
+      se = c(0.02, .05)
+    ),
+    dist = "beta"
+  )
R> utility_tbl
\end{Sinput}
\begin{Soutput}
   state_id mean   se
1:        1  0.8 0.02
2:        2  0.6 0.05
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> medcost_tbl <- stateval_tbl(
+    data.table(
+      state_id = states$state_id,
+      mean = c(2000, 9500),
+      se = c(2000, 9500)
+    ),
+    dist = "gamma"
+  )
R> medcost_tbl
\end{Sinput}
\begin{Soutput}
   state_id mean   se
1:        1 2000 2000
2:        2 9500 9500
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> drugcost_tbl <- stateval_tbl(drugcost_dt, dist = "fixed")
R> drugcost_tbl
\end{Sinput}
\begin{Soutput}
    strategy_id state_id time_id time_start time_stop   est
 1:           1        1       1       0.00      0.25  2000
 2:           1        1       2       0.25       Inf  2000
 3:           1        2       1       0.00      0.25  1500
 4:           1        2       2       0.25       Inf  1200
 5:           2        1       1       0.00      0.25 12000
 6:           2        1       2       0.25       Inf 12000
 7:           2        2       1       0.00      0.25  1500
 8:           2        2       2       0.25       Inf  1200
 9:           3        1       1       0.00      0.25 15000
10:           3        1       2       0.25       Inf 15000
11:           3        2       1       0.00      0.25  1500
12:           3        2       2       0.25       Inf  1200
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> transmod_data <- expand(hesim_dat, by = c("strategies", "patients"))
R> head(transmod_data)
\end{Sinput}
\begin{Soutput}
   strategy_id patient_id strategy_name soc new1 new2      age female
1:           1          1           SOC   1    0    0 46.26366      1
2:           1          2           SOC   1    0    0 50.49314      1
3:           1          3           SOC   1    0    0 35.52785      1
4:           1          4           SOC   1    0    0 58.88309      0
5:           1          5           SOC   1    0    0 53.66930      0
6:           1          6           SOC   1    0    0 53.40432      1
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> transmod <- create_IndivCtstmTrans(wei_fits, transmod_data,
+    trans_mat = tmat, n = n_samples, uncertainty = "normal",
+    clock = "reset", start_age = patients$age)
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> utilitymod <- create_StateVals(utility_tbl, n = n_samples, 
+    hesim_data = hesim_dat)
R> drugcostmod <- create_StateVals(drugcost_tbl, n = n_samples,
+    time_reset = TRUE, hesim_data = hesim_dat)
R> medcostmod <- create_StateVals(medcost_tbl, n = n_samples,
+    hesim_data = hesim_dat)
R> costmods <- list(Drug = drugcostmod, Medical = medcostmod)
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> ictstm <- IndivCtstm$new(trans_model = transmod, 
+    utility_model = utilitymod, cost_models = costmods)
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> ictstm$sim_disease(max_age = 100)
R> head(ictstm$disprog_)
\end{Sinput}
\begin{Soutput}
   sample strategy_id patient_id grp_id from to final time_start time_stop
1:      1           1          1      1    1  3     1   0.000000 11.183651
2:      1           1          2      1    1  2     0   0.000000  8.058198
3:      1           1          2      1    2  3     1   8.058198 12.794488
4:      1           1          3      1    1  2     0   0.000000 15.250551
5:      1           1          3      1    2  3     1  15.250551 23.791357
6:      1           1          4      1    1  3     1   0.000000  6.047286
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> library("ggplot2")
R> autoplot(ictstm$stateprobs_, labels = labs_indiv, ci = FALSE) 
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> hesim_dat$patients <- data.table(
+    patient_id = 1:4,
+    grp_id = c(1, 1, 2, 2),
+    patient_wt = rep(1/4, 4),
+    age = c(55, 65, 55, 65),
+    female = c(1, 1, 0, 0),
+    grp_name = rep(c("Female", "Male"), each = 2)
+  )
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> onc_pfs_os <- as_pfs_os(onc3, 
+    patient_vars = c("patient_id", "female", "age", "strategy_name"))
R> onc_pfs_os[patient_id %in% c(1, 2)]
\end{Sinput}
\begin{Soutput}
   patient_id female      age strategy_name pfs_time pfs_status os_status
1:          1      0 59.85813         New 2 2.420226          1         1
2:          2      0 62.57282         New 2 7.497464          0         0
     os_time
1: 14.620258
2:  7.497464
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> onc_pfs_os_soc <- onc_pfs_os[strategy_name == "SOC"]
R> fit_pfs_soc_wei <- flexsurvreg(Surv(pfs_time, pfs_status) ~ female,
+    data = onc_pfs_os_soc, dist = "weibull")
R> fit_os_soc_wei <- flexsurvreg(Surv(os_time, os_status) ~  female,
+    data = onc_pfs_os_soc, dist = "weibull")
R> psmfit_soc_wei <- partsurvfit(
+    flexsurvreg_list(pfs = fit_pfs_soc_wei, os = fit_os_soc_wei), 
+    data = onc_pfs_os_soc)
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> drugcost_tbl <- stateval_tbl(
+    drugcost_dt[time_start ==  0][, time_start := NULL],
+    dist = "fixed"
+  )
R> drugcost_tbl
\end{Sinput}
\begin{Soutput}
   strategy_id state_id   est
1:           1        1  2000
2:           1        2  1500
3:           2        1 12000
4:           2        2  1500
5:           3        1 15000
6:           3        2  1500
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> survmods_data <- expand(hesim_dat, by = c("strategies", "patients"))
R> head(survmods_data)
\end{Sinput}
\begin{Soutput}
   strategy_id patient_id strategy_name soc new1 new2 grp_id patient_wt age
1:           1          1           SOC   1    0    0      1       0.25  55
2:           1          2           SOC   1    0    0      1       0.25  65
3:           1          3           SOC   1    0    0      2       0.25  55
4:           1          4           SOC   1    0    0      2       0.25  65
5:           2          1         New 1   0    1    0      1       0.25  55
6:           2          2         New 1   0    1    0      1       0.25  65
   female grp_name
1:      1   Female
2:      1   Female
3:      0     Male
4:      0     Male
5:      1   Female
6:      1   Female
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> survmods_params <- create_params(psmfit_soc_wei, n = n_samples, 
+    uncertainty = "bootstrap", max_errors = 5, silent = TRUE)
R> survmods_params$pfs$coefs$scale <- cbind(survmods_params$pfs$coefs$scale,
+    coef_pfs_wei)
R> survmods_params$os$coefs$scale <- cbind(survmods_params$os$coefs$scale,
+    coef_os_wei)
R> survmods_params$pfs$coefs$scale[1:2, ]
\end{Sinput}
\begin{Soutput}
     (Intercept)     female      new1      new2
[1,]    1.784666 -0.1364781 0.1814189 0.2654431
[2,]    1.776743 -0.1173777 0.1390351 0.2907570
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> survmods_data[, ("(Intercept)") := 1]
R> survmods <- create_PsmCurves(survmods_params, input_data = survmods_data)
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> psm <- Psm$new(survival_models = survmods, utility_model = utilitymod,
+    cost_models = costmods)
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> times <- seq(0, 30, by = .1)
R> psm$sim_survival(t = times)
R> head(psm$survival_)
\end{Sinput}
\begin{Soutput}
   sample strategy_id patient_id grp_id patient_wt curve   t  survival
1:      1           1          1      1       0.25     1 0.0 1.0000000
2:      1           1          1      1       0.25     1 0.1 0.9998540
3:      1           1          1      1       0.25     1 0.2 0.9993126
4:      1           1          1      1       0.25     1 0.3 0.9982992
5:      1           1          1      1       0.25     1 0.4 0.9967670
6:      1           1          1      1       0.25     1 0.5 0.9946815
\end{Soutput}
\end{Schunk}

\begin{Schunk}
\begin{Sinput}
R> autoplot(psm$survival_, 
+    labels = c(labs_cohort, list(curve = c("PFS" = 1, "OS" = 2))),
+    ci = TRUE, ci_style = "ribbon")
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> psm$sim_stateprobs()
R> psm$stateprobs_[sample == 1 & patient_id == 1 & state_id == 2 & t == 12]
\end{Sinput}
\begin{Soutput}
   sample strategy_id patient_id grp_id patient_wt state_id  t      prob
1:      1           1          1      1       0.25        2 12 0.3215069
2:      1           2          1      1       0.25        2 12 0.3934037
3:      1           3          1      1       0.25        2 12 0.4148810
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> library("msm")
R> qinit <- matrix(0, nrow = 3, ncol = 3)
R> qinit[1, 2] <-  0.28; qinit[1, 3] <-  0.013; qinit[2, 3] <-  0.10
R> msm_fit <- msm(state_id ~ time, subject = patient_id, 
+    data = onc3p[strategy_name == "SOC"], exacttimes = FALSE,
+    covariates = ~ age + female, qmatrix = qinit, gen.inits = FALSE)
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> params_rr <- list(
+    lrr_12_est = c(soc = log(1), new1 = log(.80), new2 = log(.71)),
+    lrr_12_se = c(soc = 0, new1 = .03, new2 = .04),
+    lrr_13_est = c(soc = log(1), new1 = log(.90), new2 = log(.85)),
+    lrr_13_se = c(soc = 0, new1 = .02, new2 = .03)
+  )  
R> params_rr_def <- define_rng({
+    list(
+      rr_12 = lognormal_rng(lrr_12_est, lrr_12_se),
+      rr_13 = lognormal_rng(lrr_13_est, lrr_13_se)
+    )}, 
+    n = n_samples
+  )
R> params_rr_rng <- eval_rng(params_rr_def, params_rr)
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> x_rr <- as.matrix(transmod_data[, .(soc, new1, new2)])
R> rr <- cbind(
+    xbeta(x_rr, params_rr_rng$rr_12),
+    xbeta(x_rr, params_rr_rng$rr_13)
+  )
R> head(rr) 
\end{Sinput}
\begin{Soutput}
         [,1]      [,2]
[1,] 1.000000 1.0000000
[2,] 1.000000 1.0000000
[3,] 1.000000 1.0000000
[4,] 1.000000 1.0000000
[5,] 0.833283 0.9039595
[6,] 0.833283 0.9039595
\end{Soutput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> pmat <- apply_rr(pmat_soc, rr = rr, index = list(c(1, 2), c(1, 3)))
R> tprobs <- tparams_transprobs(pmat, tpmat_id)
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> cdtstm <- CohortDtstm$new(trans_model = transmod, 
+    utility_model = psm$utility_model, cost_models = psm$cost_models)
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> wtp <- seq(0, 250000, 500) 
R> cea_ictstm <- cea(ce_sim_ictstm, dr_costs = .03, dr_qalys = .03, k = wtp)
R> cea_pw_ictstm <- cea_pw(ce_sim_ictstm, comparator = 1, dr_qalys = .03, 
+    dr_costs = .03, k = wtp)
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> icer(cea_pw_ictstm, k = 100000, labels = labs_indiv) %>%
+    format()
\end{Sinput}
\begin{Soutput}
             Outcome                     New 1                    New 2
1: Incremental QALYs         0.52 (0.16, 0.90)        0.93 (0.58, 1.27)
2: Incremental costs   62,551 (51,685, 70,389) 90,010 (77,342, 100,581)
3:   Incremental NMB -11,003 (-42,132, 21,247)  3,223 (-28,582, 33,456)
4:              ICER                   121,345                   96,543
\end{Soutput}
\end{Schunk}
